\documentclass[10pt, twocolumn, twoside, letterpaper]{IEEEtran}

\usepackage[activate={true, nocompatibility}, final, tracking=true, kerning=true, spacing=true, factor=1100, stretch=10, shrink=10]{microtype}
% \linespread{0.9}

\makeatletter
\def\ps@IEEEtitlepagestyle{
  \def\@evenfoot{}
}

% \def\ps@IEEEtitlepagestyle{
%   \def\@oddfoot{\mycopyrightnotice}
%   \def\@evenfoot{}
% }
% \def\mycopyrightnotice{
%   {\footnotesize
%   \begin{minipage}{\textwidth}
%   \centering
%   978-1-7281-7693-2/20/\$31.00 \copyright2020 IEEE
%   \end{minipage}
%   }
% }

\ifCLASSINFOpdf
   \usepackage[pdftex]{graphicx}
\else
   \usepackage[dvips]{graphicx}
\fi

\ifCLASSOPTIONcompsoc
  \usepackage[caption=false, font=normalsize, labelfont=sf, textfont=sf]{subfig}
\else
  \usepackage[caption=false, font=footnotesize]{subfig}
\fi

\usepackage{amsmath}
\usepackage{bm}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{stfloats}
\usepackage{url}
\usepackage{siunitx}
\usepackage{fancyref}

\usepackage{geometry}
\geometry{letterpaper, top=0.7in, bottom=0.7in, left=0.65in, right=0.65in}

\input{glossary}

\usepackage[style=ieee, doi=false, isbn=false, url=false, maxbibnames=1, minbibnames=1, maxcitenames=1, mincitenames=1, backend=biber, defernumbers=false]{biblatex}
\addbibresource{./bibtex/bib/Biblio.bib}

\begin{document}

\title{PET/CT Respiratory Motion Correction With a Single Attenuation Map Using NAC Derived Deformation Fields}

\pagestyle{plain}
\pagenumbering{gobble}

\author{Alexander~C.~Whitehead,~\IEEEmembership{Student~Member,~IEEE,}
        Ander~Biguri,
        Nikos~Efthimiou,~\IEEEmembership{Member~IEEE},
        Kuan-Hao~Su,
        Scott~D.~Wollenweber,~\IEEEmembership{Senior~Member~IEEE,}
        Charles~W.~Stearns,~\IEEEmembership{Fellow,~IEEE,}
        Brian~F.~Hutton,~\IEEEmembership{Senior~Member,~IEEE,}
        Jamie~R.~McClelland
        and~Kris~Thielemans,~\IEEEmembership{Senior~Member,~IEEE}%
        
    % \vspace{-1.0cm}

    % \thanks{Manuscript received November 29, 2021.}
    \thanks{Alexander~C.~Whitehead, Ander~Biguri, Brian~F.~Hutton and Kris~Thielemans are with the Institute of Nuclear Medicine, University College London, UK (contact: \texttt{alexander.whitehead.18@ucl.ac.uk}).}%
    \thanks{Alexander~C.~Whitehead and Jamie~R.~McClelland are with the Centre for Medical Image Computing, University College London, UK.}%
    \thanks{Nikos~Efthimiou is with the Department Radiology, Perelman School of Medicine, University of Pennsylvania, USA.}%
    \thanks{Kuan-Hao~Su, Scott~D.~Wollenweber and Charles~Stearns are with Molecular Imaging and Computed Tomography Engineering, GE Healthcare, USA.}%
    \thanks{This research is supported by GE Healthcare, the NIHR UCLH Biomedical Research Centre and the UCL EPSRC Centre for Doctoral Training in Intelligent, Integrated Imaging in Healthcare (i4health) grant (EP/L016478/1). The software used was partly produced by the Computational Collaborative Project in Synergistic PET-MR Reconstruction, CCP PET-MR, UK EPSRC grant (EP/M022587/1) and the CCP on Synergistic Biomedical Imaging, CCP SyneRBI, UK EPSRC grant (EP/T026693/1).}%
    \thanks{Jamie~R.~McClelland is supported by a Cancer Research UK Centres Network Accelerator Award grant (A21993) to the ART-NET consortium and a CRUK Multi-disciplinary grant (CRC 521).}%
}

\maketitle
\IEEEpeerreviewmaketitle

\begin{abstract}
    Respiratory motion correction is beneficial in positron emission tomography. Different strategies for handling attenuation correction in conjunction with motion correction exist. In clinical practice, usually a single attenuation map is available, derived from computed tomography in one respiratory state. This can introduce an unwanted bias (through misaligned anatomy) into the motion correction algorithm. This paper builds upon previous work which suggested that non-attenuation corrected data was suitable for motion estimation, through the use of motion models, if time-of-flight data are available. Here, the previous work is expanded upon by incorporating attenuation correction in an iterative process. Non-attenuation corrected volumes are reconstructed using ordered subset expectation maximisation and used as input for motion model estimation. A single attenuation map is then warped to the volumes, using the motion model, the volumes are attenuation corrected, after which another motion estimation and correction cycle is performed. For validation, $4$-Dimensional Extended Cardiac Torso simulations are used, for one bed position, with a field of view including the base of the lungs and the diaphragm. The output from the proposed method is evaluated against a non-motion corrected reconstruction of the same data visually, using a profile as well as standardised uptake value analysis. Results indicate that motion correction of inter-respiratory cycle motion is possible with this method, while accounting for attenuation deformation.% Future research includes the possibility of directly incorporating the motion model estimation into the reconstruction algorithm as well as  attempting to simultaneously estimate deformations for the attenuation map as well as the activity distribution.
\end{abstract}

% \vspace{-0.5cm}

\input{body}

% \vspace{-0.5cm}

\AtNextBibliography{\scriptsize}
\printbibliography

\end{document}
